\documentclass[12pt]{article}
\usepackage[letterpaper, hmargin=0.75in, vmargin=0.75in]{geometry}
\usepackage{courier,float,graphicx,listings,tikz,url,verbatimbox}

\lstset{basicstyle=\footnotesize\ttfamily}

\usetikzlibrary{arrows,automata,shapes}
\tikzstyle{block} = [rectangle, draw, fill=blue!20,
    text width=5em, text centered, rounded corners, minimum height=2em]


\begin{document}
\title{SE465-001\\Assignment 3}
\author{Kevin Carruthers (20463098), {\tt kcarruth@uwaterloo.ca}}
\date{March 30, 2015}
\maketitle

\section*{Question 1}
% p = (a ∧ b) ∨ (b ∧ c) ∨ (a ∧ c)
% p_a = b xor c
% p_b = a xor c
% p_c = a xor b
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c||c||c|c|c|}
\hline
  & a & b & c & p & $p_a$ & $p_b$ & $p_c$ \\ \hline
2 & T & T & F & T & T     & T     & F     \\ \hline
3 & T & F & T & T & T     & F     & T     \\ \hline
6 & F & T & F & F & T     & F     & T     \\ \hline
7 & F & F & T & F & T     & T     & F     \\ \hline
1 & T & T & T & T & F     & F     & F     \\ \hline
4 & T & F & F & F & F     & T     & T     \\ \hline
5 & F & T & T & T & F     & T     & T     \\ \hline
8 & F & F & F & F & F     & F     & F     \\ \hline
\end{tabular}
\end{table}

\paragraph{GACC.} Pairs of rows that satisfy GACC: For $p_a$, we can select any of $\{(2, 5), (2, 8), (3, 5), (3, 8)\}$. For $p_b$, we can select any of $\{(2, 3), (2, 8), (5, 3), (5, 8)\}$. For $p_c$, we can select any of $\{(3, 2), (3, 8), (5, 2), (5, 8)\}$.
\paragraph{CACC.} Pairs of rows that satisfy CACC: For $p_a$, we can select any of $\{(2, 5), (2, 8), (3, 5), (3, 8)\}$. For $p_b$, we can select any of $\{(2, 3), (2, 8), (5, 3), (5, 8)\}$. For $p_c$, we can select any of $\{(3, 2), (3, 8), (5, 2), (5, 8)\}$.
\paragraph{RACC.} Pairs of rows that satisfy RACC: There are no valid test combinations for any of our predicates $p_a, p_b, p_c$.


\section*{Question 2}
\paragraph{size of s2, completeness.} No: \ttfamily{s2 = null;}\rmfamily{}.
\paragraph{size of s2, disjointness.} Yes.
\paragraph{relation, completeness.} Yes.
\paragraph{relation, disjointnessness.} No. \ttfamily{s1 = \{1, 2, 3\}, s2 = \{1, 2, 3\}}\rmfamily{}.
\paragraph{Base choice TRs.} Since there are two characteristics which each have two partitions, there would result four test requirements.


\section*{Question 3}
\paragraph{Mozilla bug.} Problems with this report:
\begin{description}
\item [Title is unclear]: What does the bugreport author mean by ``shown wrong''.
\item [Description is unclear]: The bugreport author uses unclear language, eg. what does ``address of the first one for each of the others'' mean?
\item [No expected results]: The author listed only the actual results, not what he should be expecting.
\item [No version information]: The author did not include the version number of the product showing the issue.
\end{description}

To improve the quality of this report, we should fix the above issues. A better report would be:
\begin{verbnobox}[\scriptsize]
Title:
Incorrect recipient addresses are listed when mail is sent to multiple recipients.

Description:
When sending mail to multiple recipients either directly or by cc'ing them, Mozilla Mail
only shows the first address for each recipient, as opposed to the address it was sent to.

Reproducible: Always
Steps to Reproduce:
1. Create user with email addresses: <random_address@email.com>, <your_email@email.com>.
2. Send message to <your_email@email.com>.
3. Open the recieved message in Mozilla Mail.
4. Look at the recipients-list.
Expected Results: <your_email@email.com>
Actual Results: <random_address@email.com>

This bug was found in build 2001112104.
\end{verbnobox}

\paragraph{HashTable bug report.}
\begin{verbnobox}[\scriptsize]
Title:
HashTable put function does not update existing element.

Description:
When `put`ing an element which already exists, the associated element is not updated.

Reproducible: Always
Steps to Reproduce:
1. Create a hashtable with size >= 1
2. Put a key-value pair into the table.
3. Put a key-value pair with the same key and a different value.
4. Examine the table.
Expected Results: table contains: key-new_value
Actual Results: table contains: key-old_value

Test Code:
HashTable table = new HashTable(1);
table.put(new Integer(3), new Integer(7));
table.put(new Integer(3), new Integer(42));
table.output();
Expected: 3-42
Actual: 3-7
\end{verbnobox}

\end{document}
